---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# package6

<!-- badges: start -->
[![R-CMD-check](https://github.com/DSCI-310/DSCI-310-Group-6-Package/workflows/R-CMD-check/badge.svg)](https://github.com/DSCI-310/DSCI-310-Group-6-Package/actions)
[![codecov](https://codecov.io/gh/DSCI-310/DSCI-310-Group-6-Package/branch/main/graph/badge.svg?token=QRIHLUGBLT)](https://codecov.io/gh/DSCI-310/DSCI-310-Group-6-Package)
<!-- badges: end -->

The goal of package6 is to encapsulate useful helper functions used for data analysis projects similar to [New Taipei City Real Estate Value Prediction](https://github.com/DSCI-310/DSCI-310-Group-6).

<br/>

## Installation

You can install the development version of package6 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSCI-310/DSCI-310-Group6-Package")
```
<br/>

## Usage

```{r setup, include=FALSE}
library(package6)
```

### `format_column_names()`
Sometimes raw data set have column names with blank spaces in the column names.
```{r}
df <- data.frame(`col Name1`= c(1,2),`col Name2` = c("3", "4"),  check.names = FALSE)
df
```

it is generally a good idea to remove the blank spaces. This is what `base::gsub()` do.

``` {r}
names(df) <- gsub(" ", "_", names(df))
df
```

Notice how `gsub()` requires three arguments and modifies the original data frame.Also the return value is not a data frame. `package6::format_column_names()` requires only one argument. It does not modify the original data frame and returns the data frame with formatted column names.

``` {r}
df <- data.frame(`col Name1`= c(1,2),`col Name2` = c("3", "4"),  check.names = FALSE)
formatted_df <- format_column_names(df)
formatted_df
```

### `split_data(dataset, train_perc, vs_prec, test_perc)`
To split a data set/ date frame into 3 parts:train data, test data and variable selection data
```{r}
df <- mtcars
glimpse(df)
```

Let's start with mtcars data frame

``` {r}
train<-split_data(mtcars)$train
cv<-split_data(mtcars)$cv
test<-split_data(mtcars)$test
glimpse(train)
glimpse(cv)
glimpse(test)
```

### `cal_rmse(x,y)`
To calculate RMSE 
```{r}
predicted = c(12, 5, 19, 3)
actual = c(11, 4, 15, 6)

cal_rmse(predicted, actual)

```

<br/>

## Dependencies

  | Package      | Version |
  | ------------ | ------- |
  | tidyverse    |   	1.3.1 |

<br/>

## License

